PANCHANGE_analysis

### 2021-04-23 PANCHANGE_analysis.Rmd
added sensitivity analyses dropping NBR from retro regressions

#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
#kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

@@

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
##KT

@@

>>>>

```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
#kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

@@

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

@@

## Sensitivity: retrospective regression (excluding NBR)

retrospective dataset, dropping NBR (which includes edgi)
```{r make no nbr dat}

dat.retro.noNBR <- dat.retro %>%
  filter(Sample != "NBR" & 
           Sample != "EDGI")

### GAD
#### Original
```{r retro original gad}

gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

#### sensitivity
```{r retro sensitivty no NBR gad}

gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro.noNBR")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

### PHQ
#### Original
```{r retro original phq}

phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

#### sensitivity
```{r retro sensitivty no NBR phq}

phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro.noNBR")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

### PCL
#### Original
```{r retro original pcl}

pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                                                               explan_var = "pcl.sum_score_retro",
                                                               data_set = "dat.retro")
kable(pcl_retro_model1b_explan_estimates)
pcl_retro_model1b_explan_estimates

#### sensitivity
```{r retro sensitivty no NBR pcl}

pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                                                               explan_var = "pcl.sum_score_retro",
                                                               data_set = "dat.retro.noNBR")
kable(pcl_retro_model1b_explan_estimates)
pcl_retro_model1b_explan_estimates
